---
title: "hw10"
author: "張立勳"
output: html_document
---
#Basic calculation 
```{r}
1+1 
3-5 
4*6 
12/4 
3^4 
31%%7 
31%/%7 
``` 
#Elements storage 
##vector 
###use ***c()*** function to collect a list of numbers into a vector
```{r}
x<-c(5,7,8) 
x 
``` 
###vectors can be joined together 
```{r}
y<-c(x,6:1)
y
``` 
###extract elements from vectors 
```{r}
y[5]
y[c(1,3,5)]
y[-2]
y[-(3:5)]
``` 
###vector arithmetic 
```{r}
z<-x-4
z
``` 
```{r}
z*2
z^2
x^z
y%%2:4
``` 
###simple patterned vectors 
```{r}
seq(1,9,by=2)
rep(3,5)
rep(seq(2,6,2),2)
rep(c(1,4),c(3,2))
rep(c(1,2,4),each=3)
``` 
###missing values and other special values 
the missing value symbol is ***NA*** 
```{r}
evens<-NULL
evens[seq(2,10,2)]<-seq(2,10,2)
evens
``` 
a value which is "not a number" is ***NAN***,usually 0/0
```{r}
x<-c(0,7,8)
x/x
``` 
***Inf***,usually 1/0 
```{r}
1/x
``` 
***numeric(0)*** is a numeric vector of length 0 
```{r}
x[0.4]
x[1.8]
``` 
###character vector 
```{r}
x<-c("red","yellow","blue")
y<-c(x,"green")
y
``` 
an attempt to mix data types in a vector will lead to a result that numbers will be converted to the character type 
```{r}
z<-c(y,1)
z
``` 
to take substrings,use ***substr(x,start,stop)*** 
```{r}
substr(z,2,4)
``` 
to concatenate characters 
```{r}
paste(x," flower","s",sep="")
``` 
***collapse*** parameter allows all the components of the resulting vector to be collapsed into a single string 
```{r}
paste(x," flowers",collapse=", ")
``` 
###factors and levels 
```{r}
x<-c("control","treatment","control","test","treatment")
y<-factor(x)
y
``` 
to see the levels 
```{r}
levels(y)
``` 
to see how the levels coded 
```{r}
as.integer(y)
``` 
the original data can be rewrite as 
```{r}
levels(y)[as.integer(y)]
``` 
###other 
to detect where are missing values 
```{r}
is.na(evens)
``` 
##matrix 
```{r}
m<-matrix(1:6,nrow=2,ncol=3)
m
m[1,2]
m[5]
m[1,]
m[,1]
``` 
##array 
```{r}
a<-array(1:24,c(3,4,2))
``` 
##data frame 
```{r}
colors<-c("red","yellow","blue","green")
numbers<-c(1,2,3,4)
c.a.n<-data.frame(colors,numbers,more.n=5:8)
c.a.n
``` 

#Plot statistical graphics 
##high-level 
###barchart
```{r}
barplot(VADeaths)
```

###dotchart 
```{r}
dotchart(VADeaths)
```
 
###piechart
```{r}
pie(VADeaths)
```
 
###histogram
```{r}
hist(VADeaths)
```
 
###box plot
```{r}
boxplot(VADeaths)
```
 
###scatterplot
```{r}
plot(VADeaths)
```
 
###QQplot
```{r}
#qqplot(VADeaths)
```

##low-level 
###add points
```{r,echo=FALSE}
#help(plot)
#points(2,2)
```


