---
title: "hw10"
author: "張立勳"
output: html_document
---
#Basic calculation 
```{r}
1+1 
3-5 
4*6 
12/4 
3^4 
31%%7 
31%/%7 
``` 
#Elements storage 
##vectors 
###use ***c()*** function to collect a list of numbers into a vector
```{r}
x<-c(5,7,8) 
x 
``` 
###vectors can be joined together 
```{r}
y<-c(x,6:1)
y
``` 
###extract elements from vectors 
```{r}
y[5]
y[c(1,3,5)]
y[-2]
y[-(3:5)]
``` 
###vector arithmetic 
```{r}
z<-x-4
z
``` 
```{r}
z*2
z^2
x^z
y%%2:4
``` 
###simple patterned vectors 
```{r}
seq(1,9,by=2)
rep(3,5)
rep(seq(2,6,2),2)
rep(c(1,4),c(3,2))
rep(c(1,2,4),each=3)
``` 
###missing values and other special values 
the missing value symbol is ***NA*** 
```{r}
evens<-NULL
evens[seq(2,10,2)]<-seq(2,10,2)
evens
``` 
a value which is "not a number" is ***NAN***,usually 0/0
```{r}
x<-c(0,7,8)
x/x
``` 
***Inf***,usually 1/0 
```{r}
1/x
``` 
***numeric(0)*** is a numeric vector of length 0 
```{r}
x[0.4]
x[1.8]
``` 
###character vectors 
```{r}
x<-c("red","yellow","blue")
y<-c(x,"green")
y
``` 
an attempt to mix data types in a vector will lead to a result that numbers will be converted to the character type 
```{r}
z<-c(y,1)
z
``` 
to take substrings,use ***substr(x,start,stop)*** 
```{r}
substr(z,2,4)
``` 
to concatenate characters 
```{r}
paste(x," flower","s",sep="")
``` 
***collapse*** parameter allows all the components of the resulting vector to be collapsed into a single string 
```{r}
paste(x," flowers",collapse=", ")
``` 
###factors and levels 
```{r}
x<-c("control","treatment","control","test","treatment")
y<-factor(x)
y
``` 
to see the levels 
```{r}
levels(y)
``` 
to see how the levels coded 
```{r}
as.integer(y)
``` 
the original data can be rewrite as 
```{r}
levels(y)[as.integer(y)]
``` 
###others 
to detect where are missing values 
```{r}
is.na(evens)
``` 
##matrices 
```{r}
m<-matrix(1:6,nrow=2,ncol=3)
m
m[1,2]
m[5]
m[1,]
m[,1]
``` 
##arrays 
```{r}
a<-array(1:24,c(3,4,2))
``` 
##data frames 
```{r}
colors<-c("red","yellow","blue","green")
numbers<-c(1,2,3,4)
c.a.n<-data.frame(colors,numbers,more.n=5:8)
c.a.n
names(c.a.n)
c.a.n$numbers
``` 
##lists 
```{r}
x<-c(3,2,3)
y<-c(7,7)
list(x=x,y=y)
``` 
##elementary built-in functions 
```{r}
x=c(seq(1,10),25)
sum(x)
mean(x)
median(x)
sd(x)
var(x)
summary(x)
``` 
##logical vectors and relational operators 
###boolean algebra 
```{r}
A<-TRUE
B<-FALSE
```
not A 
```{r}
!A
``` 
A and B 
```{r}
A&B
``` 
A or B 
```{r}
A|B
``` 
###logical operations 
```{r}
a<-c(TRUE,FALSE,FALSE,TRUE)
b<-c(13,7,8,2)
b[a]
sum(a)
``` 
0 is taken as ***FALSE*** in boolean algebra 
```{r}
a&(b-2)
``` 
###relational operators 
```{r}
a<-c(3,6,9)
a>4
a==4
a>=4
a!=4
a[a>4]
b<-c(4,6,8)
a<b
a[a<b]
```
#Simulation 
##binomial 
* pmf

$dbinom(x,size,prob)$ 
```{r}
dbinom(4,6,0.5)
```

* cdf 

$pbinom(x,size,prob)$
```{r}
pbinom(4,6,0.5)
```

* quantiles 

$qbinom(quantiles,size,prob)$
```{r}
qbinom(0.89,6,0.5)
```

* simulation 

$rbinom(n,size,prob)$
```{r}
defectives<-rbinom(24, 15, 0.1)
defectives
```
##poisson
* pmf 
 
$dpois(x,lambda)$ 
```{r}
dpois(3,0.5)
```

* cdf 

$ppois(x,lambda)$
```{r}
ppois(3,0.5)
```

* quantiles 

$qpois(quantiles,lambda)$
```{r}
qpois(0.25,0.5)
```

* simulation 

$rpois(n,lambda)$
```{r}
rpois(10,3.7)
``` 
##exponential 
* pdf 
 
$dexp(x,rate)$ 
```{r}
dexp(3,0.5)
```

* cdf 

$pexp(x,rate)$
```{r}
pexp(3,0.5)
```

* quantiles 

$qexp(quantiles,rate)$
```{r}
qexp(0.25,0.5)
```


* simulation 

$rexp(n,rate)$
```{r}
rexp(10,3.7)
``` 
##normal 
* pdf 
 
$dnorm(x,mean,sd)$ 
```{r}
dnorm(3,2,3)
```

* cdf 

$pnorm(x,mean,sd)$
```{r}
pnorm(3,2,3)
```

* quantiles 

$qnorm(quantiles,mean,sd)$
```{r}
qnorm(0.25,2,3)
```


* simulation 

$rnorm(n,mean,sd)$
```{r}
rnorm(10,2,3)
``` 
#Plot statistical graphics 
##high-level 
###curve 
```{r}
curve(expr=sin,from=0,to=6*pi)
```
 
###barchart 
```{r}
barplot(VADeaths)
```
 
###dotchart 
```{r}
dotchart(VADeaths)
```
 
###piechart 
```{r}
pie(VADeaths)
```
 
###histogram 
```{r}
hist(VADeaths)
```
 
###box plot 
```{r}
boxplot(VADeaths)
```
 
###scatterplot 
```{r}
plot(VADeaths)
```
 
###QQplot 
```{r}
x<-rnorm(1000)
y<-rnorm(1000)
qqplot(x,y,main="X and Y are the same")
```
 
##low-level 
* points(x,y,...) **adds points**

* lines(x,y,...) **adds line segments**

* text(x,y,labels,..) **adds text into the graph**

* abline(a,b,...) **adds the line y=ax+b**

* abline(h=y,...) **adds a horizontal line**

* abline(v=x,...) **adds a vertical line**

* polygon(x,y,...) **adds a polygon**

* segments(x0,y0,x1,y1,...) **draws line segments**

* arrows(x0,y0,x1,y1,...) **draws arrows**

* symbols(x,y,...) **draws circles,squares,...**

* legend(x,y,legend,...) **draws a legend**

* title(main,sub,xlab,ylab,...) **adds a main title, a sub-title, an x-axis label and a y-axis label**

* mtext(text,side,line,...) **draws text in the margins**

* axis(side,at,labels,...) **adds an axis to the plot**

* box(...) **adds a box around the plot region**

```{r}
par(mar=c(5,5,5,5)+0.1)
plot(c(1,9),c(0,50),type="n",xlab="",ylab="")
text(6,40,"Plot Region")
points(6,20)
text(6,20,"(6,20)",adj=c(0.5,2))
mtext(paste("Margin",1:4),side=1:4,line=3)
mtext(paste("Line",0:4),side=1,line=0:4,at=3,cex=0.6)
mtext(paste("Line",0:4),side=2,line=0:4,at=15,cex=0.6)
mtext(paste("Line",0:4),side=3,line=0:4,at=3,cex=0.6)
mtext(paste("Line",0:4),side=4,line=0:4,at=15,cex=0.6)

```
 
#Programming 
##the ***for()*** loop 
***for(name){command}***
```{r}
Fibonacci<-numeric(12)
Fibonacci[1]<-Fibonacci[2]<-1
for (i in 3:12){
  Fibonacci[i]<-Fibonacci[i-2]+Fibonacci[i-1]
}
Fibonacci
``` 
##the ***if()*** statement 
***if (conditon){commands when TRUE}else{commands when FALSE}***
```{r}
x<-3
if (x>2){
  y<-2*x
}else{
  y<-3*x
}
y
``` 
##the ***while()*** loop 
***while(conditon){statements}***
```{r}
Fib1<-1
Fib2<-1
Fibonacci<-c(Fib1,Fib2)
while (Fib2<300){
  Fibonacci<-c(Fibonacci,Fib2)
  oldFib2<-Fib2
  Fib2<-Fib1+Fib2
  Fib1<-oldFib2
}
Fibonacci
``` 